Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements

### 2025-04-15 Submission.Rmd
Updating results

cr_burn_m1 <- lm(burnout ~ scale(overall.challenge_center), modreg)
#summary(cr_burn_m1)

cr_burn_m2 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
#summary(cr_burn_m2)

cr_burn_m3 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_burn_m3)

@@

cr_stress_m1 <- lm(stress ~ scale(overall.challenge_center), modreg)
#summary(cr_stress_m1)

cr_stress_m2 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_stress_m2)

cr_stress_m3 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_stress_m3)

@@

cr_eng_m1 <- lm(engagement ~ scale(overall.challenge_center), modreg)
#summary(cr_eng_m1)

cr_eng_m2 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_eng_m2)

cr_eng_m3 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_eng_m3)

@@

hr_burn_m1 <- lm(burnout ~ scale(overall.hindrance_center), modreg)
#summary(hr_burn_m1)

hr_burn_m2 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_burn_m2)

hr_burn_m3 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_burn_m3)

@@

hr_stress_m1 <- lm(stress ~ scale(overall.hindrance_center), modreg)
#summary(hr_stress_m1)

hr_stress_m2 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_stress_m2)

hr_stress_m3 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_stress_m3)

@@

hr_eng_m1 <- lm(engagement ~ scale(overall.hindrance_center), modreg)
#summary(hr_eng_m1)

hr_eng_m2 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_eng_m2)

hr_eng_m3 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_eng_m3)

@@

papaja::apa_table(regtable, 
              caption = "Moderated regression summary of outcomes regressed on challenges and resources",
              escape=FALSE,
              note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
```

@@

H3a predicted that both resources and challenges would predict engagement. Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout). Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.  Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation (Hypothesis 4a). Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

papaja::apa_table(regtable,
                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
```
### Hindrances, Resources, and Outcomes

We also explored whether there was an interaction between hindrance demands and resources on the outcome variables. Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions. First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2` [see Table \@ref(tab:hind-resource-table)]. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`. An interaction between hindrances and resources was not found.

>>>>

cr_burn_m1 <- lm(burnout ~ scale(overall.challenge), modreg)
#summary(cr_burn_m1)

cr_burn_m2 <- lm(burnout ~ scale(overall.challenge) + scale(overall.resource), modreg)
#summary(cr_burn_m2)

cr_burn_m3 <- lm(burnout ~ scale(overall.challenge) + scale(overall.resource) + scale(overall.challenge*overall.resource), modreg)
#summary(cr_burn_m3)

@@

cr_stress_m1 <- lm(stress ~ scale(overall.challenge), modreg)
#summary(cr_stress_m1)

cr_stress_m2 <- lm(stress ~ scale(overall.challenge) + scale(overall.resource), modreg)
#summary(cr_stress_m2)

cr_stress_m3 <- lm(stress ~ scale(overall.challenge) + scale(overall.resource) + scale(overall.challenge*overall.resource), modreg)
#summary(cr_stress_m3)

@@

cr_eng_m1 <- lm(engagement ~ scale(overall.challenge), modreg)
#summary(cr_eng_m1)

cr_eng_m2 <- lm(engagement ~ scale(overall.challenge) + scale(overall.resource), modreg)
#summary(cr_eng_m2)

cr_eng_m3 <- lm(engagement ~ scale(overall.challenge) + scale(overall.resource) + scale(overall.challenge*overall.resource), modreg)
#summary(cr_eng_m3)

@@

hr_burn_m1 <- lm(burnout ~ scale(overall.hindrance), modreg)
#summary(hr_burn_m1)

hr_burn_m2 <- lm(burnout ~ scale(overall.hindrance) + scale(overall.resource), modreg)
#summary(hr_burn_m2)

hr_burn_m3 <- lm(burnout ~ scale(overall.hindrance) + scale(overall.resource) + scale(overall.hindrance*overall.resource), modreg)
#summary(hr_burn_m3)

@@

hr_stress_m1 <- lm(stress ~ scale(overall.hindrance), modreg)
#summary(hr_stress_m1)

hr_stress_m2 <- lm(stress ~ scale(overall.hindrance) + scale(overall.resource), modreg)
#summary(hr_stress_m2)

hr_stress_m3 <- lm(stress ~ scale(overall.hindrance) + scale(overall.resource) + scale(overall.hindrance*overall.resource), modreg)
#summary(hr_stress_m3)

@@

hr_eng_m1 <- lm(engagement ~ scale(overall.hindrance), modreg)
#summary(hr_eng_m1)

hr_eng_m2 <- lm(engagement ~ scale(overall.hindrance) + scale(overall.resource), modreg)
#summary(hr_eng_m2)

hr_eng_m3 <- lm(engagement ~ scale(overall.hindrance) + scale(overall.resource) + scale(overall.hindrance*overall.resource), modreg)
#summary(hr_eng_m3)

@@

papaja::apa_table(regtable, 
              caption = "Moderated regression summary of outcomes regressed on challenges and resources",
              escape=FALSE,
              note="* = p < .05; ** = p < .01, coefficients are unstandardized")
```

@@

H3a predicted that both resources and challenges would predict engagement. Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout). Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized. First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.  Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation (Hypothesis 4a). Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

papaja::apa_table(regtable,
                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01, coefficients are unstandardized")
```
### Hindrances, Resources, and Outcomes

We also explored whether there was an interaction between hindrance demands and resources on the outcome variables. Sum scores for the predictors were used here again. First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2` [see Table \@ref(tab:hind-resource-table)]. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`. An interaction between hindrances and resources was not found.

### 2025-04-15 Submission.tex
Updating results

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** & 0.15 ** & \\
 & 2 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** &  & \\
 &  & Challenge X Resource & -0.07 * & 0.16 ** & 0.01 *\\
Stress & 1 & Challenge & 0.12 &  & \\
 &  & Resource & -0.06 & 0.01 & \\
 & 2 & Challenge & 0.12 &  & \\
 &  & Resource & -0.06 &  & \\
 &  & Challenge X Resource & 0.02 & 0.01 & 0.00\\
Burnout & 1 & Challenge & 0.28 ** &  & \\
 &  & Resource & -0.12 & 0.04 ** & \\
 & 2 & Challenge & 0.28 ** &  & \\
 &  & Resource & -0.12 &  & \\
 &  & Challenge X Resource & 0.05 & 0.04 ** & 0.00\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered}
\end{tablenotes}

@@

H3a predicted that both resources and challenges would predict engagement. Table \ref{tab:chal-resource-table} summarizes the results for engagement (as well as stress and burnout). Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\). Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation (Hypothesis 4a). Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Hindrance & -0.11 ** &  & \\
 &  & Resource & 0.35 ** & 0.17 ** & \\
 & 2 & Hindrance & -0.10 ** &  & \\
 &  & Resource & 0.34 ** &  & \\
 &  & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
Stress & 1 & Hindrance & 0.08 * &  & \\
 &  & Resource & 0.01 & 0.01 * & \\
 & 2 & Hindrance & 0.16 ** &  & \\
 &  & Resource & -0.10 &  & \\
 &  & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
Burnout & 1 & Hindrance & 0.09 * &  & \\
 &  & Resource & 0.10 * & 0.04 ** & \\
 & 2 & Hindrance & 0.13 * &  & \\
 &  & Resource & 0.03 &  & \\
 &  & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered}
\end{tablenotes}

@@

We also explored whether there was an interaction between hindrance demands and resources on the outcome variables. Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions. First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj. \(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\) {[}see Table \ref{tab:hind-resource-table}{]}. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13. An interaction between hindrances and resources was not found.

>>>>

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** & 0.15 ** & \\
 & 2 & Challenge & 0.12 &  & \\
 &  & Resource & 0.57 ** &  & \\
 &  & Challenge X Resource & -0.4 * & 0.16 ** & 0.01 *\\
Stress & 1 & Challenge & 0.12 &  & \\
 &  & Resource & -0.06 & 0.01 & \\
 & 2 & Challenge & 0.08 &  & \\
 &  & Resource & -0.1 &  & \\
 &  & Challenge X Resource & 0.09 & 0.01 & 0.00\\
Burnout & 1 & Challenge & 0.28 ** &  & \\
 &  & Resource & -0.12 & 0.04 ** & \\
 & 2 & Challenge & 0.13 ** &  & \\
 &  & Resource & -0.26 &  & \\
 &  & Challenge X Resource & 0.29 & 0.04 ** & 0.00\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized}
\end{tablenotes}

@@

H3a predicted that both resources and challenges would predict engagement. Table \ref{tab:chal-resource-table} summarizes the results for engagement (as well as stress and burnout). Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized. First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\). Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation (Hypothesis 4a). Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Hindrance & -0.11 ** &  & \\
 &  & Resource & 0.35 ** & 0.17 ** & \\
 & 2 & Hindrance & -0.07 ** &  & \\
 &  & Resource & 0.37 ** &  & \\
 &  & Hindrance X Resource & -0.06 & 0.17 ** & 0.00\\
Stress & 1 & Hindrance & 0.08 * &  & \\
 &  & Resource & 0.01 & 0.01 * & \\
 & 2 & Hindrance & 0.66 ** &  & \\
 &  & Resource & 0.30 &  & \\
 &  & Hindrance X Resource & -0.77 ** & 0.04 ** & 0.03 **\\
Burnout & 1 & Hindrance & 0.09 * &  & \\
 &  & Resource & 0.10 * & 0.04 ** & \\
 & 2 & Hindrance & 0.46 * &  & \\
 &  & Resource & 0.29 &  & \\
 &  & Hindrance X Resource & -0.5 ** & 0.05 ** & 0.01 **\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized}
\end{tablenotes}

@@

We also explored whether there was an interaction between hindrance demands and resources on the outcome variables. Sum scores for the predictors were used here again. First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj. \(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\) {[}see Table \ref{tab:hind-resource-table}{]}. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13. An interaction between hindrances and resources was not found.
